\sysfull

### 2017-08-07 paper/evaluation.tex
added text explaining result in Figure 9

We now proceed with the evaluation of task coalescing mechanism of \sys.

Expected results:
\begin{itemize}
	\item performance for each application comparing bars for Chain, no coalescing/hand-tasked, coalescing/hand-tasked, no-coalescing/compiler, coalescing/compiler. Performance depicted, normalized to one of the configurations (probably Chain). This plot will cover most of the eval dimensions that we care about.
	\item Sensitivity plot---show amount of task merged, time to completion, overhead (in terms of task-size/cap-size sweep (remember we can vary either with approximately the same effect)), energy consumed. All experiments for fixed power, at 3 distances with wireless power, compared against Chain for 3 task/cap size configurations
\end{itemize}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{Performance of \sys's  tasks coalescing mechanism compared to virtual task size equal to one (per application) at multiple WISP to RFID reader antenna distances.\todo{Replace "coal" with "coalescing", "No-coal" with "No coalescing"; use markers in addition to color; decide on uniform naming for apps (either all small or capitalized)}{Amjad}}
	\label{fig:coalescing}
\end{figure}

Experimental evaluation of task coalescing mechanism under intermittent power of \sys is given in Figure~\ref{fig:coalescing}. For each application we measured execution time (with and without task coalescing) at \{20, 40, 60\}\,cm distance between RFID antenna and WISP and when WISP was powered directly from FET. Each measurement was repeated x times per each distance/application. From the result we clearly see an enormous benefit of coalescing, especially at large WISP to RFID reader antenna distance ($\approx$56\% for cem, 100\% for sort and $\approx$400\% for bc). At each distance, \sys coalescing mechanism provided faster execution times compared to non-coalescing case. \todo{Discuss different shapes per app}{Amjad}

Measured size of tasks for each application is given in Figure~\ref{fig:aveVirtuTaskSize}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{Average virtual task size (measured in real task unit\todo{Define real task unit}{Amjad}) of the virtual task sizes that the coalescing algorithm used to accomplished the applications at a WISP to RFID reader distance of 60\,cm.\todo{Please rewrite this sentence}{Amjad}}
	\label{fig:aveVirtuTaskSize}
\end{figure}

expected results:
\begin{itemize}
	\item performance for each application comparing bars for Chain, no coalescing/hand-tasked, coalescing/hand-tasked, no-coalescing/compiler, coalescing/compiler. Performance depicted, normalized to one of the configurations (probably Chain). This plot will cover most of the eval dimensions that we care about.
	\item Sensitivity plot---show amount of task merged, time to completion, overhead (in terms of task-size/cap-size sweep (remember we can vary either with approximately the same effect)), energy consumed. All experiments for fixed power, at 3 distances with wireless power, compared against Chain for 3 task/cap size configurations
\end{itemize}
